Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Document
Work in progress.

    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    We previously used to generate a new random % In a previous work (reference) - M
    set of solutions, with the cost of losing all evolution knowledge.

@@

        % Start by stating the similarities with a GA, in the sense that 
        % all individuals have a genotype (chromosome)that is a list of values.  - M

>>>>

    In previous work, we introduced an algorithm inspired by the biological
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    In a previous work \cite{Felix-Saul2022} we used to generate a new random
    set of solutions, with the cost of losing all evolution knowledge.

@@

        This algorithm was inspired by the traditional Genetic Algorithm,
        meaning that all individuals have a genotype (chromosome) that is a
        list of values. We calculate the individual's fitness with the
        evaluation function and do crossover and mutation to the population.
        What makes our strategy different is that we don't use the concept of
        evolutionary generations. We manage our set of solutions as a whole
        that continuously evolve over time. Allowing individuals of different
        ages to breed and generate offspring, as it happens in nature. The
        crossover and mutation execute as independent processes that randomly
        affect the individuals.
